### 2021-04-13 sections/model_overview/main.tex
Finish writing of section and add referecne

\begin{equation}
    \max_{T_i} \quad P(W_i < \textit{Target})
\end{equation}

@@

\begin{equation}
    \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
\end{equation}

On the other side of the spectrum, the distributor has its own choices 
to make and its own goals to satisfy.
The set of strategies it has can be defined as the different ways that it can 
distribute individuals to the two queueing system.
Therefore, unlike the queueing systems, the distributor has a 
continuous set of strategies that goes from \( 0\% - 100\% \). 
For example, it may choose to send \(35\%\) of its individuals to the first 
queueing system and \(65\%\) to the second one.
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distribution service is the proportion of lost individuals.
Equation \ref{eq:obj-distribution-service} can be used to capture a mixture 
between the two objectives.

\begin{equation}\label{eq:obj-distribution-service}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

@@

% PAR: COMBINED FORMULATION (Figure of 3-player game)
% Intro
% Payoff matrices??

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](H1){\(H_1\)};
        \node[anchor=north](H1_d1) at (3, 2){.};
        \node[anchor=north](H1_d2) at (3, -2){.};

        \path[->] (H1) edge node {}(H1_d1);
        \path[->] (H1) edge node {}(H1_d2);
        \path (H1_d1) edge [bend left] node {}(H1_d2);
        \path (H1_d1) [dashed] edge node {}(H1_d2);

        \node[anchor=north](H2) at (4.1, 0){\(H_2\)};
        \node[anchor=north](H2_d1) at (6.9, 2){.};
        \node[anchor=north](H2_d2) at (6.9, -2){.};

        \path[->] (H2) edge node {}(H2_d1);
        \path[->] (H2) edge node {}(H2_d2);
        \path(H2_d1) edge [bend left] node {}(H2_d2);

        \node[anchor=north](A) at (7.8, 0){\(A\)};
        \node[anchor=north](A_d1) at (10.8, 2){.};
        \node[anchor=north](A_d2) at (10.8, -2){.};

        \path[->] (A) edge node {}(A_d1);
        \path[->] (A) edge node {}(A_d2);
        \path(A_d1) edge [bend left] node {}(A_d2);
    \end{tikzpicture}
    \caption{}
\end{figure}

\begin{table}[ht]
    \centering
    A = 
    \begin{tabular}{|l|l|l|l|}
    \hline
    \( U_{1,1}^A \) & \( U_{1,2}^A \) & \dots & \( U_{1,N_B}^A \) \\ \hline
    \( U_{2,1}^A \) & \( U_{2,2}^A \) & \dots & \( U_{2,N_B}^A \) \\ \hline
    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
    \( U_{N_A,1}^A \) & \( U_{N_A,2}^A \) & \dots & \( U_{N_A,N_B}^A \) \\ \hline
    \end{tabular}
\end{table}

\begin{table}[ht]
    \centering
    B = 
    \begin{tabular}{|l|l|l|l|}
    \hline
    \( U_{1,1}^B \) & \( U_{1,2}^B \) & \dots & \( U_{1,N_B}^B \) \\ \hline
    \( U_{2,1}^B \) & \( U_{2,2}^B \) & \dots & \( U_{2,N_B}^B \) \\ \hline
    \vdots & \vdots & \( \ddots \) & \vdots \\ \hline
    \( U_{N_A,1}^B \) & \( U_{N_A,2}^B \) & \dots & \( U_{N_A,N_B}^B \) \\ \hline
    \end{tabular}
\end{table}

>>>>

\begin{equation}
    \arg \max_{T_i} \quad P(W_i < \textit{Target})
\end{equation}

@@

\begin{equation}\label{eq:obj-queueing-systems}
    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < \textit{Target}) \right)^2
\end{equation}

On the other side of the spectrum, the distributor has its own choices 
to make and its own goals to satisfy.
The set of strategies it has can be defined as the different ways that it can 
distribute individuals to the two queueing system.
Therefore, unlike the queueing systems, the distributor has a 
continuous set of strategies that goes from \( 0\% - 100\% \). 
For example, it may choose to send \(35\%\) of its individuals to the first 
queueing system and \(65\%\) to the second one.
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distribution service is the proportion of lost individuals.
Equation \ref{eq:obj-distributor} can be used to capture a mixture 
between the two objectives.

\begin{equation}\label{eq:obj-distributor}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

@@

% PAR: COMBINED FORMULATION (Figure of 3-player game)
% Intro
Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor}, an
imperfect information extensive form game may arise. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players \cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each player chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen strategies are, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked.

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](HA){\(H_A\)};
        \node[anchor=north](HA_d1) at (3, 2){.};
        \node[anchor=north](HA_d2) at (3, -2){.};

        \path[->] (HA) edge node {}(HA_d1);
        \path[->] (HA) edge node {}(HA_d2);
        \path (HA_d1) edge [bend left] node {}(HA_d2);
        \path (HA_d1) [dashed] edge node {}(HA_d2);

        \node[anchor=north](HB) at (4.1, 0){\(H_B\)};
        \node[anchor=north](HB_d1) at (6.9, 2){.};
        \node[anchor=north](HB_d2) at (6.9, -2){.};

        \path[->] (HB) edge node {}(HB_d1);
        \path[->] (HB) edge node {}(HB_d2);
        \path(HB_d1) edge [bend left] node {}(HB_d2);

        \node[anchor=north](D) at (7.8, 0){\(D\)};
        \node[anchor=north](D_d1) at (10.8, 2){.};
        \node[anchor=north](D_d2) at (10.8, -2){.};

        \path[->] (D) edge node {}(D_d1);
        \path[->] (D) edge node {}(D_d2);
        \path(D_d1) edge [bend left] node {}(D_d2);
    \end{tikzpicture}
    \caption{Imperfect information Extensive Form Game between the distributor 
    and the 2 queueing systems}
    \label{fig:imperfect-info-game}
\end{figure}

Figure \ref{fig:imperfect-info-game} illustrates such a game works. The first 
queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
chooses its own threshold, without knowing the strategy of \(H_A\), and finally
the distributor makes its choice. Note here that the dotted line represents the
fact that \(H_B\) is unaware of the state of the game when making its own 
decisions. The game can thus be partitioned into a normal form game between the
two queueing systems and finding the distributor's best choice.

In order to define the normal form game the two payoff matrices of the players 
are required. From equation \ref{eq:obj-queueing-systems} the utilities of the
players can be formulated as:

\begin{equation}
    U_{T_1, T_2}^i = \quad -\left( 
        \hat{P} - P(W_i < \textit{Target}) 
    \right)^2
\end{equation}

Consequently, the payoff matrices of the game can be populated by these 
utilities:

\begin{equation} \label{eq:payoff-matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix},
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}

Based on the choice of strategy of these two players the distributor will then 
make its own choice of proportion of individuals to send to each system.
